Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex

In the space  of functional languages, improving  space efficiency has
been  mainly  studied  as  a compile  time  activity.  Either  through
rewriting                methods                such                as
deforestation~\cite{wadler88deforest,gill93ashort,chitil99deforest},
sharing  analysis   based  reallocation~\cite{jones89compile},  region
based  analysis~\cite{tofte98region}, or  through insertion  of compile
time              nullifying              statements              such
as~\cite{inoue88analysis,lee05static,Hamilton}.    The  compile   time
marking approaches all rely on an efficient and precise alias analysis
and in the absence of it cannot provide notable improvement.

>>>>

In the space  of functional languages, improving  space efficiency has
been  mainly  studied as  a  compile  time activity.   Either  through
rewriting                methods                such                as
deforestation~\cite{wadler88deforest,gill93ashort,chitil99deforest},
sharing  analysis   based  reallocation~\cite{jones89compile},  region
based analysis~\cite{tofte98region},  or through insertion  of compile
time              nullifying              statements              such
as~\cite{inoue88analysis,lee05static,Hamilton}.    The  compile   time
marking approaches all rely on an efficient and precise alias analysis
and in the  absence of it cannot provide  notable improvement. Another
important approach  advocated by  Hofmann~\cite{HofmannJ03} is  to use
linear  typing to  analyze  first-order programs  for  heap usage  and
annotated  them. The  system  then uses  these  annotations to  re-use
allocated memory  cells instead  of requesting  for newer  cells. This
requires the  user to write programs  in a specific way  and hence may
not be practical
